### 2019-03-22 4_implementation.tex
Edits.

One challenge in implementing Task Bench for such a wide variety of
systems is that the capabilities of the systems vary considerably. For
example, some systems are \emph{implicitly parallel}, and provide some
form of parallelism discovery from sequential programs, whereas others
are \emph{explicitly parallel} and require users to specify the
parallelism in the program. As a rule of thumb, we aim for the Task
Bench implementations to be representative of how actual applications
would be written in the respective systems. Places where the Task
Bench implementations may be unidiomatic are noted below.

@@

In all cases, members of the respective programming systems' teams
were consulted during the development and evaluation of the
corresponding Task Bench implementations. Their insight was invaluable
to ensure that we provide the highest level of quality in the Task
Bench implementations for each system.

@@

PaRSEC~\cite{PARSEC13} is a task-based programming system which
supports two distinct programming models: \emph{parameterized task
  graphs} (PTG) and \emph{dynamic task discovery} (DTD)~\cite{PARSEC_DTD}. 
PTG is a data flow model, where programmers write applications 
in a concise description of all data flows by describing tasks 
and how data flows between tasks. This creates a compressed algebraic
representation of the task graph, which is then transformed into C 
code by PaRSEC source-to-source compiler. PTG is therefore a more limited
programming model, but can potentially provide better performance
because the graph description is amenable to static analysis and can
be pruned efficiently for better horizontally scalable execution.

@@

The PaRSEC build-in 2D block cyclic matrix is used to store data. 
A matrix is divided into M by N tiles where N equals to the width of
task graphs and M varies from 2 to the height of task graphs depends
on the optimization level of alleviating write-after-read depdenencies. 
Tiles are distributed across nodes in pre-defined patterns, 
and can be passed to tasks on other nodes, but
can only be written on the node where the data is originally
allocated. In our Task Bench implementation, each task writes to a
tile as output, and these tiles are passed as inputs to the
subsequent set of tasks. As in the OmpSs and OpenMP implementations,
the task launch code uses a switch statement as the PaRSEC API assumes
tasks have a fixed number of dependencies.

% FIXME: What does PaRSEC call regions?

@@

Tasks in Realm are executed in a deferred manner, with dependencies
between tasks explicitly defined by \emph{events} passed from one task
to another. Realm's data model supports regions which live on a single
node. Data must be explicitly copied, and the copies synchronized with
tasks via events.

@@

StarPU~\cite{StarPU11} is a task-based system that supports an DTD
programming model similar to PaRSEC. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies, and manual
elision of tasks on unrelated nodes to provide horizontal scalability.
A simplified version of 2D block cyclic matrix from the Chameleon 
project~\cite{Chameleon} is used to describe data of tasks in 
our Task Bench implementation.

>>>>

One challenge in implementing Task Bench for such a wide variety of
systems is that the capabilities of the systems vary considerably. For
example, some systems are \emph{implicitly parallel}, and provide some
form of parallelism discovery from sequential programs, whereas others
are \emph{explicitly parallel} and require users to specify the
parallelism in the program. As a rule of thumb we aim for the Task
Bench implementations to be representative of how actual applications
would be written in the respective systems. Places where the Task
Bench implementations may be unidiomatic are noted below.

@@

In all cases, members of the respective programming systems' teams
were consulted during the development and evaluation of the
corresponding Task Bench implementations. Their insight was invaluable
in helping to ensure that we provide the highest level of quality in the Task
Bench implementations for each system.

@@

PaRSEC is a task-based programming system which supports two distinct
programming models: \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}.  PTG is a dataflow model in which programmers
write a concise, algebraic description of the tasks and dataflows in
the program. This compressed representation is expanded into a full
task graph by a source-to-source compiler. PTG is therefore a more
limited programming model, but can potentially provide better
performance because the graph description is amenable to static
analysis and can be pruned efficiently for better horizontal
scalability.

@@

Data in PaRSEC is stored in a built-in matrix data structure with a 2D block cyclic distribution. 
The Task Bench implementation divides this matrix into $M$ by $N$ tiles where $N$ equals to the width of
the task graph and $M$ varies from 2 to the height of the task graph depending
on optimizations performed to alleviate write-after-read depdenencies. 
Tiles are distributed across nodes in pre-defined patterns, 
and can be passed to tasks on other nodes, but
can only be written on the node where the data is originally
allocated. In our Task Bench implementation, each task writes to a
tile as output, and these tiles are passed as inputs to the
subsequent sets of tasks. As in the OmpSs and OpenMP implementations,
the task launch code uses a switch statement as the PaRSEC API assumes
tasks have a fixed number of dependencies.

@@

Tasks in Realm are executed in a deferred manner, with dependencies
between tasks explicitly defined by \emph{events} passed from one task
to another. Realm's data model supports \emph{regions} of memory which live on a single
node. Data must be explicitly copied, and the copies synchronized with
tasks via events.

@@

StarPU~\cite{StarPU11} is a task-based system that supports an DTD
programming model similar to PaRSEC. Our Task Bench implementation in
StarPU is very similar to PaRSEC, including the use of a switch
statement to handle dynamic numbers of task dependencies, and manual
elision of tasks on unrelated nodes to provide horizontal scalability.
A simplified version of the 2D block cyclic matrix from the Chameleon 
project~\cite{Chameleon} is used to describe the data produced by tasks in 
our Task Bench implementation.
